Supplementary Materials for ``COATi: statistical pairwise alignment of protein coding sequences''

### 2024-01-01 figures/fig-aln.tex
Update supplementary materials

\node (titlePrankMacse) [below right=2.6cm and -1.8cm of titleBiology] {\textbf{b) PRANK (codon) and MACSE}};
% prank codon --gaprate=0.01
\matrix (prank-macse) [aln,below right=-1mm and -4.6cm of titlePrankMacse] {
   & Ser & His     & Lys & Gly  & Arg & Ser &           & Asp & Ala & \\
A: & TCC & CAT     & AAG & GGG  & CGG & TCG &\verb|---| & GAC & GCC & \verb|---|\\
D: & TCC & CA\e{G} & \verb|---| & GGG & CGG & TC\e{C} & CCG & GCC & GCC & ACG\\
   & Ser & Gln     &            & Gly     & Arg & Ser   & Pro  & Asp & Ala & Thr\\
};
\draw [indel,phase0] (prank-macse-2-8.north west) rectangle (prank-macse-3-8.south east);
\draw [indel,phase0] (prank-macse-2-11.north west) rectangle (prank-macse-3-11.south east);
\draw [indel,phase0] (prank-macse-2-4.north west) rectangle (prank-macse-3-4.south east);

>>>>

\node (titlePrankMacse) [below right=2.6cm and -1.8cm of titleBiology] {\textbf{b) PRANK (codon) and MACSE}};
% prank codon --gaprate=0.01
\matrix (prank-macse) [aln,below right=-1mm and -4.6cm of titlePrankMacse] {
   & Ser & His     & Lys & Gly  & Arg & Ser &           & Asp & Ala & \\
A: & TCC & CAT     & AAG & GGG  & CGG & TCG &\verb|---| & GAC & GCC & \verb|---|\\
D: & TCC & CA\e{G} & \verb|---| & GGG & CGG & TC\e{C} & CCG & GAC & GCC & ACG\\
   & Ser & Gln     &            & Gly     & Arg & Ser   & Pro  & Asp & Ala & Thr\\
};
\draw [indel,phase0] (prank-macse-2-8.north west) rectangle (prank-macse-3-8.south east);
\draw [indel,phase0] (prank-macse-2-11.north west) rectangle (prank-macse-3-11.south east);
\draw [indel,phase0] (prank-macse-2-4.north west) rectangle (prank-macse-3-4.south east);
